Copulas reveal complex and informative dependencies propagating throughout ecology

### 2019-05-16 Paper.Rmd
reading as csv

\noindent \emph{The number of words in the main text (excluding abstract, acknowledgements, references, table and figure legends):} 7493

@@

\noindent \emph{The number of references:} 31

@@

```{r read_BivMS_soilCN_data,echo=F}
d<-readRDS("Data/RaCA_soilorganicC_soiltotalN_stocks100cm.RDS")
d<-d[,c("SOCstock100","TSNstock100")] #raw soilCN data
BivMS_res_Loecke<-readRDS("./Results/fitting_results/BivMS_soilCN.RDS")
```

>>>>

\noindent \emph{The number of words in the main text (excluding abstract, acknowledgements, references, table and figure legends):} 7509

@@

\noindent \emph{The number of references:} 34

@@

```{r read_BivMS_soilCN_data,echo=F}
d<-read.csv("./Data/SoilCN/SoilCNdata.csv")
rownames(d)<-d$X
d<-d[,-1]
d<-d[,c("SOCstock100","TSNstock100")] #raw soilCN data
BivMS_res_Loecke<-readRDS("./Results/fitting_results/BivMS_soilCN.RDS")
```
